Sequence assembly

### 2025-04-08 episodes/sequence-assembly.Rmd
Started with assembly, fixed a typo in the phylogenetics

Sequence assembly means the alignment and merging of reads in order to reconstruct the original sequence. The assembly of a genome from short sequencing reads can take a while. We will therefore run this process only for two genomes.

@@

Start the interactive session, go to the `molepi` subfolder, create a `results/assembly` subfolder. Then go to the folder containing the fastq files.

```bash
interactive -A uppmax2024-2-10 -M snowy -t 04:00:00
cd /proj/g2020004/nobackup/3MK013/<username>/molepi/
mkdir results/assembly
cd data/trimmed_fastq
```

>>>>

Sequence assembly means the alignment and merging of reads in order to reconstruct the original sequence. The assembly of a genome from short sequencing reads can take a while. We will therefore run this process for two genomes only.

@@

Start the interactive session, go to the `molepi` subfolder, create a `results/assembly` subfolder. Then go to the folder containing the fastq files (`data/trimmed_fastq`) that you created in the previous tutorial.

::: hint

You know this by now... 
```bash
interactive
cd
mkdir
```

:::::::::

Project is `uppmax2025-3-4`, cluster is `snowy`

```bash
interactive <project> <cluster> <time>
cd /proj/g2020004/nobackup/3MK013/<username>/molepi/
mkdir results/assembly
cd data/trimmed_fastq
```

::: instructor

```bash
interactive -A uppmax2025-3-4 -M snowy -t 04:00:00
cd /proj/g2020004/nobackup/3MK013/<username>/molepi/
mkdir results/assembly
cd data/trimmed_fastq
```

### Running SKESA in a loop
